{\itE}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-11 draft.tex
Revised the plan.

%%%%%%%%% TITLE
\title{Multiple Kernelized Correlation Filters based High Speed Target Following}

@@

\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF
\item Re-detection for re-initialization
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item Conclusion
\end{itemize}

>>>>

%%%%%%%%% TITLE
\title{{\itE}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz}

@@

\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
\item Re-detection for re-initialization
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item {\it E}nKCF, Naive{\it E}nKCF, ${\it E}nKCF_{+RD}$, LCT, DSST,
  vanilla-KCF w/ a fixed scale, KCF w/ three different scales, STC,
\begin{itemize}
\item DTB-70: w/ and w/o motion estimation,
\item UAV data, https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx
\item VOT
\end{itemize}
\item Conclusion
\end{itemize}
